---
title: "Modelling Media Type"
author: "Hans-Peter Bakker (BKKHAN001)"
date: "5/3/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(nlme)
```

```{r readObjects}
type_frame <- readRDS("type_frame.rds")
```

# MODELING

## RADIO
```{r radio_explore}
radio_grouped <- groupedData(radios ~ year | category, data = type_frame)
plot(radio_grouped) # check
radio_list <- lmList(radios ~ I(year - mean(year)) | category, data = radio_grouped)
plot(intervals(radio_list))
```

# model 1 radio
```{r radio_model_1}

radio_lme1 <- lme(radio_list)
summary(radio_lme1)
plot(radio_lme1)
qqnorm(radio_lme1)
plot(radio_lme1, resid(.) ~ year | category)
intervals(radio_lme1)
random.effects(radio_lme1)
```

would appear that the residual distribution is OK but not great. Will consider a model that allows different variances by level of category.

# model 2 radio
```{r radio_model_2}
radio_lme2 <- update(radio_lme1, weights = varIdent(form = ~ 1|category) )
summary(radio_lme2)
plot(radio_lme2)
qqnorm(radio_lme2)
```

The diagnostic plots appear to show an improvement.

comparing models 1 and 2 with an anova:

```{r radio_compare_1n2}
anova(radio_lme1, radio_lme2)
plot(compareFits(ranef(radio_lme1), ranef(radio_lme2)), mark = c(0,0))
```
would appear that model 2 is a considerable improvement on model 1.???

considering a
Could consider non-linear options...but visuals don't really support it.....

visualise its fitted values in .R script

### Meaning:


## NEWSPAPERS
```{r news_explore}
news_grouped <- groupedData(news ~ year | category, data = type_frame)
plot(news_grouped) # check
news_list <- lmList(news ~ I(year - mean(year)) | category, data = news_grouped)
plot(intervals(news_list))
```
does look like linear ok, although in some cases growth curves may be appropriate

```{r news_model_1}
news_lme1 <- lme(news_list)
summary(news_lme1)
plot(news_lme1)
qqnorm(news_lme1)
plot(news_lme1, resid(.) ~ year | category)
plot(news_lme1, category ~ resid(.), abline = 0)
plot(news_lme1, resid(., type = "p") ~ fitted(.) | category, id = 0.05, adj = -0.3)
plot(news_lme1, radios ~ fitted(.), id = 0.05, adj = -0.3)
qqnorm(news_lme1, ~ resid(.) | category)
plot(news_lme1, resid(.) ~ radios | category)

comp <- compareFits(coef(news_list), coef(news_lme1))
plot(comp, mark = fixef(news_lme1))

plot(comparePred(news_list, news_lme1, length.out = 2, layout = c(8,4), between = list(y = c(0,0.5))))
plot(compareFits(ranef(radio_lme1), ranef(radio_lme2)), mark = c(0,0))
# intervals(news_lme1)
# random.effects(news_lme1)
```
not good residual plot and not good qqnorm either.




## MAGAZINES
```{r}
mags_grouped <- groupedData(mags ~ year | category, data = type_frame)
plot(mags_grouped) # check
mags_list <- lmList(mags ~ I(year - mean(year)) | category, data = mags_grouped)
plot(intervals(mags_list))
mags_lme <- lme(mags_list)
summary(mags_lme)
```

## TV
```{r}
tvs_grouped <- groupedData(tvs ~ year | category, data = type_frame)
plot(tvs_grouped) # check
tvs_list <- lmList(tvs ~ I(year - mean(year)) | category, data = tvs_grouped)
plot(intervals(tvs_list))
tvs_lme <- lme(tvs_list)
summary(tvs_lme)
```

## INTERNET
```{r}
internet_grouped <- groupedData(internets ~ year | category, data = type_frame)
plot(internet_grouped) # check
internet_list <- lmList(internets ~ I(year - mean(year)) | category, data = internet_grouped)
plot(intervals(internet_list))
internet_lme <- lme(internet_list)
summary(internet_lme)
```